Assessing Usability of Tor Browser

### 2015-04-10 PETS2015-paper/paper.tex
Typo.
remove red comments

\title{Assessing Usability of Tor Browser}
\numberofauthors{1}
\author{
 \alignauthor David Fifield\textsuperscript{1} and Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,2}, David Wagner\textsuperscript{1}\\
   \vspace{0.5em}
   \affaddr{\textsuperscript{1}University of California, Berkeley, \{fifield,lnl,egelman,daw\}@cs.berkeley.edu}, \\
   \affaddr{\textsuperscript{2}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
}

%\numberofauthors{1}
%\author{
% \alignauthor Anonymous\\
%   \vspace{0.5em}
%   \affaddr{Some Place}
%}
\maketitle

\begin{abstract}
Our talk will be about ongoing experiments aimed at
assessing and improving the usability of Tor Browser.
There have been been no major usability evaluations of
Tor Browser since the introduction of the 4.0 series,
which introduced radical UI changes.
We briefly describe the results of a completed study
that examined the download, install, and 
and basic browsing behaviors.
This study uncovered a number of bugs and stopping points
and has already effected concrete change in the browser.
We will describe a future study aimed at
evaluating Tor Browser as a tool for censorship circumvention, isolating specific browser features in depth in the process. 
{\color {red}LL: I don't know how to say this, but I want the fact that we are evaluating it from a different standpoint --ie as a censorship circumvention tool, to stand out more. Also, we spend more abstract real estate talking about the first experiment rather than our design, which I think should be flipped. But for right now, I can't think of what exactly to fix so I'll look at this later.}
We solicit feedback on our experimental design
and the specific features of the browser that we are testing.
\end{abstract}

\keywords{Privacy, Security, User Studies, Anonymity, Tor} % NOT required for Proceedings

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item{Corporate network.}
A simulation of a enterprise or educational firewall.
Blocks all services but HTTP, HTTPS, and DNS.
Certain non-work-related domains, like youtube.com and torproject.org,
are blocked by DNS and HTTP inspection.
Blocked requests are redirected to a block page.
\item{DNS-only censor.}
This censor injects false replies to DNS queries
for forbidden domain names (DNS poisoning),
but does not do deep packet inspection on TCP streams.
Unlike the corporate censor, this censor allows protocols
other than HTTP, HTTPS, and DNS.
\item{Comprehensive censor.}
Employs a variety of techniques, depending on the target.
May do DNS poisoning, IP blocking, and inspection of TCP streams
(examining the URL of HTTP requests, for example).
Some domains may be blocked by DNS and deep packet inspection;
others may additionally be blocked by IP address.
Tor relays are blocked by IP address.
Some domains, like wikipedia.org, may allow HTTP but not HTTPS.
Blocked requests fail silently (no block page).
\end{itemize}

@@

\noindent {\bfseries Experiment Execution Details} 
{\color {red} this subsection might be too much}We plan to recruit at least 120 (to 200?) users for the purpose of this study. This study will be performed at the Experimental Social Science Laboratory (Xlab) at the University of California, Berkeley. The laboratory space consists of 36 laptops with cubicle walls separating each laptop. We used individual host firewalls to simulate the censorship environments. We plan to write a browser extension to measure when users visit what websites in order to log which websites they were successfully able to visit. The total length of the experiment should be less than an hour. Participants will be compensated \$30 for their time, which is more to cover minimum wage and transportation costs.  \\

@@

During the question-and-answer session,
we will be especially interested in soliciting feedback
on these topics:
{\color {red} I feel like I am abusing bold text in this paper..}

>>>>

\title{Assessing Usability of Tor Browser}
\numberofauthors{1}
\author{
 \alignauthor David Fifield\textsuperscript{1} and Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,2}, David Wagner\textsuperscript{1}\\
   \vspace{0.5em}
   \affaddr{\textsuperscript{1}University of California, Berkeley, \{fifield,lnl,egelman,daw\}@cs.berkeley.edu}, \\
   \affaddr{\textsuperscript{2}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
}
\maketitle

% is the abstract missing some oomph? 
% I don't know how much the storyline is showing through.. or what we are testing. 
\begin{abstract}
Our talk will be about ongoing experiments aimed at
assessing and improving the usability of Tor Browser.
There have been been no major usability evaluations of
Tor Browser since the introduction of the 4.0 series,
which introduced radical UI changes.
We briefly describe the results of a completed study
that examined the download, install, and 
and basic browsing behaviors.
This study uncovered a number of bugs and stopping points
and has already effected concrete change in the browser.
We will describe a future study aimed at
evaluating Tor Browser as a tool for censorship circumvention, isolating specific browser features in depth in the process. 
We solicit feedback on our experimental design
and the specific features of the browser that we are testing.
\end{abstract}

\keywords{Privacy, Security, User Studies, Anonymity, Tor}

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item{Corporate network.}
A simulation of an enterprise or educational firewall.
Blocks all services but HTTP, HTTPS, and DNS.
Certain non-work-related domains, like youtube.com and torproject.org,
are blocked by DNS and HTTP inspection.
Blocked requests are redirected to a block page.
\item{DNS-only censor.}
This censor injects false replies to DNS queries
for forbidden domain names (DNS poisoning),
but does not do deep packet inspection on TCP streams.
Unlike the corporate censor, this censor allows protocols
other than HTTP, HTTPS, and DNS.
\item{Comprehensive censor.}
Employs a variety of techniques, depending on the target.
May do DNS poisoning, IP blocking, and inspection of TCP streams
(examining the URL of HTTP requests, for example).
Some domains may be blocked by DNS and deep packet inspection;
others may additionally be blocked by IP address.
Tor relays are blocked by IP address.
Some domains, like wikipedia.org, may allow HTTP but not HTTPS.
Blocked requests fail silently (no block page).
\end{itemize}

@@

%frame this in the sense that we are saying, ``we have this figued out. we want feedback on other things.''
\noindent {\bfseries Experiment Execution Details} 
We plan to recruit at least 120 (to 200?) users for the purpose of this study. This study will be performed at the Experimental Social Science Laboratory (Xlab) at the University of California, Berkeley. The laboratory space consists of 36 laptops with cubicle walls separating each laptop. We used individual host firewalls to simulate the censorship environments. We plan to write a browser extension to measure when users visit what websites in order to log which websites they were successfully able to visit. The total length of the experiment should be less than an hour. Participants will be compensated \$30 for their time, which is more to cover minimum wage and transportation costs.  \\

@@

During the question-and-answer session,
we will be especially interested in soliciting feedback
on these topics:
